---
output: github_document
bibliography: inst/REFERENCES.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DOSPorfolio

<!-- badges: start -->
<!-- badges: end -->

The goal of DOSPorfolio is to provide a simple interface for computing portfolio weights according to the dynamic weighting scheme from [@BODNAR21dynshrink]. 

## Installation

The development version can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Statistics-In-Portfolio-Theory/DOSportfolio")
```
## Example

This is a very simple example which shows you how use the package:
```{r example, eval=FALSE}
library(DOSPorfolio)
n <- 25*2
p <- 15
# Simulate data
data <- matrix(rt(n*p, df=5), ncol=p, nrow=n)
reallocation_points <- c(25, 42)
(portfolios <- DOSPortfolio(data, reallocation_points))
```
To read the documentation you can simply use `?DOSPortfolio`.

## TODO:

- Finish tests.
- Include test on finite fourth moment, summary function to generate table from the article?
- Setup so that the portfolio estimators can work with the `tsibble` package?
- Extend theory to mean-variance portfolio (...)

# References
