---
output: github_document
bibliography: inst/REFERENCES.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DOSPorfolio

<!-- badges: start -->
<!-- badges: end -->

The goal of DOSPorfolio is to provide a simple interface for computing portfolio 
weights according to the dynamic weighting scheme from [@BODNAR21dynshrink]. 

## Installation

The development version can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Statistics-In-Portfolio-Theory/DOSportfolio")
```

## Example

This is a very simple example which shows you how use the package:
```{r example}
library(DOSPortfolio)
n <- 25*2
p <- 15
# Simulate data
data <- sqrt(5/3) * matrix(rt(n*p, df=5), ncol=p, nrow=n)
# specify the allocation points. The DOSPortfolio class will validate what is 
# "ok" allocation periods.
reallocation_points <- c(25, 42)
(portfolios <- DOSPortfolio(data, reallocation_points))
```
The variable `portfolios` is a "DOSPortfolio" class whose documentation can be 
viewed by `?DOSPortfolio`. The constructor `DOSPortfolio()` looks for violations
against the assumptions made in the reference. Here is an example when things 
does not work

```{r example error, error=TRUE, results='asis'}
reallocation_points <- c(37, 42)
# observe that there is little data between the first and second allcoation 
# point. Its actually to little since p > n_2, e.g. 15 > 42 - 37. 

# This will cause an error
DOSPortfolio(data, reallocation_points)
```
However, by using the the argument `shrinkage_type="overlapping"` we can 
make it work!
```{r}
DOSPortfolio(data, reallocation_points, shrinkage_type = "overlapping")
```
If you want to learn to more why this is then you can have a look at the 
_"introduction"_ vignette or read the paper!

## Possible further scope:

- Create summary function so that one can construct summaries of the portfolios 
as done in [@BODNAR21dynshrink].
- Include test on finite fourth moment, summary function to generate table from 
the article?
- Setup so that the portfolio estimators can work with the `tsibble` package?
- Extend theory to mean-variance portfolio and Shrinkage estimators.

# References
