---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DOSPorfolio

<!-- badges: start -->
<!-- badges: end -->

The goal of DOSPorfolio is to provide a simple interface for computing portfolio weights according to the dynamic weighting scheme from _link when published on arxiv?_. 

## Installation

The development version can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Statistics-In-Portfolio-Theory/DOSportfolio")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(DOSPorfolio)
n <- 200*2
p <- 80
c <- p/n

# first change point in the portfolio is at the 199th observation
break_points <- c(199)
# Simulate data
data <- matrix(rt(n*p, df=5), ncol=p, nrow=n)
target_w <- ones_vec(p)/p

# Use all data to estimate r0/R0, the relative loss to the GMV portfolio
r <- r0_strategy(S_inv, S, target_w, p/n)
# estimate the GMV portfolio sequentially using non-overlapping subsamples 
w_non_overlapping(data, break_points, target_w, r)
# do the same with overlapping subsamples
w_overlapping(data, break_points, target_w, r)
```

## TODO:

- Create S3 class (and/or iterator) which enclose the overlapping/nonoverlapping portfolios.
- Setup so that the portfolio estimators can work with the `tsibble` package in a simple manner.
- Extend theory to mean-variance portfolio.
