---
title: "An introduction to the Dynamic Optimal Shrinkage Portfolio package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteIndKexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package is a collection of the methods developed in [references]()...

To install the package you need to run `devtools::install_github("Statistics-In-Portfolio-Theory/DOSportfolio")`, which demands that you have installed `devtools`. To load the package, run
```{r setup}
library(DOSPorfolio)
```

The two main functions are `DOSPortfolio::wGMVOverlapping` and `DOSPortfolio::wGMVNonOverlapping` which compute Global Mimimum Variance portfolios in a dynamic optimal shrinkage scheme. Both  S3 class for the 
The portfolio is computed using a convex combination. On the first transition, given by the first element of break points,
the function shrinks towards the target weights. On the second transition (if there exists one) we shrink towards the previous
estimate of the GMV portfolio where each weight is based of non-overlapping samples. This function estimates each GMV portfolio
using the most recent data, e.g. from the last break point to the current. The data used for the estimation of the portfolio weights
is therefore is not overlapping.


# References

 1. ...
